\thesistitle

### 2019-11-21 pldi/paper.tex
Introduction PLDI paper

\section{Introduction}
An abundant number of clone detection tools have been proposed in the literature due to the many applications and benefits of clone detection.

@@

%% Appendix
\appendix
\section{Appendix}

Text of appendix \ldots

>>>>

\section{Introduction}
Code clones argue about the duplicate code present in the source code of software systems. An abundant number of clone detection tools and techniques have been proposed in the literature due to the many applications and benefits of clone detection \cite{svajlenko2019mutation}. Clones are most often the result of code reuse by copying and pasting existing code, among other reasons \cite{roy2007survey}. Clones are often seen as harmful \cite{roy2007survey, ostberg2014automatically, juergens2009code}, but can also have positive effects on system maintainability \cite{roy2007survey, kapser2006cloning, aversano2007clones}.

Clone detection is applied in various domains. This includes (automated) refactoring, education (plagiarism detection) \cite{wahler2004clone}, (legacy code) modernization \cite{meng2013refactoring} and maintainability analysis \cite{heitlager2007practical}. For these varying purposes, many clone detection tools have been proposed: a 2013 survey by Rattan et al. \cite{rattan2013software} surveyed more than 70 clone detection tools. Comparisons show large differences in recall and precisions of these tools \cite{svajlenko2014evaluating}.

To allow easy experimentation with code clone defitions and methods, we propose a DSL to configure clone detection.

\section{Language Design}

\section{Results}

\section{Discussion}

\section{Conclusion}

\subsection{Threats to validity}

@@

%% Appendix
% \appendix
% \section{Appendix}
%
% Text of appendix \ldots
